---
title: "2022_0905_LES_data_analysis"
author: "Xin Tong"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: hide
  pdf_document:
    toc: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width= 10, fig.height= 8, fig.align = "center")
library(ggplot2) # package for plotting
library(RColorBrewer)
library(ggmap)
library(ggforce)  # facet_zoom
library(ggpubr) #stat_regline_equation
library(gridExtra) #grid.arrange
library(grid)
library(gtable) #gtable_filter
library(ggpmisc)
library(reshape2)
library(dplyr)
library(rWind) # uv2ds     derive the wind speed and direction
#library(suncalc)  # getsunlighttime
library(geosphere) # calculate the distance with the input of the latitude and longitude
library(terra)
library(ncdf4) # package for netcdf manipulation
library(ncdf4.helpers) #nc.get.time.series
library(lubridate)
library(beepr)
sapply(list.files(pattern="[.]R$", path="c:/Users/xin/Dropbox/xin/Rscripts/functions", full.names=TRUE), source)
```


\newpage
# **1. make animation to check the simulatd wind by LES model**
```{r extract les data at the same altitude}

# load airborne measurements
flight <- '0905'
wdir <- "D:/1 phd studies/1 data/Rotterdam_campaign_2022/"

data <- read.csv(paste0(wdir, flight, "/AirCore/AirCore_retrieval/AirCore_N2O_CO_CO2_CH4_CO_2022", flight, ".csv"))
# data <- mutate(data, p.H2O = H2O/18*8.3145*Tair/100,  #unit:hPa/mbar
#                pot = Tair*(1000/Ps)^0.286, ws=rWind::uv2ds(U,V)[,2], wd=rWind::uv2ds(U,V)[,1])#;names(data)
# data <- mutate(data, vir.pot = pot*(1+0.61*p.H2O/1000))
data <- data.frame(date = ISOdate(data$yyyy, data$mm, data$dd, data$hh, data$min, data$sec, tz='UTC'), data)
data$date <- round(data$date) # the second is not integer
# pick up airborne measurements for harbour areas
data <- data[
  data$date>as.POSIXlt("2022-09-06 12:24:00", tz='UTC') & data$date<as.POSIXlt("2022-09-06 12:48:00", tz='UTC'),
  c("date", "lat", "lon", "alt", "N2O.ac.ppb", "CH4.ac.ppb")
  ]
names(data)[names(data)=="lat"] <- "lat.ac";
names(data)[names(data)=="lon"] <- "lon.ac";
names(data)[names(data)=="alt"] <- "alt.ac"


# open the wrfout .nc files
library(ncdf4) # package for netcdf manipulation
library(ncdf4.helpers) #nc.get.time.series

filenames <- list.files(path = "F:/Harbour_les/les0905/", pattern = "")
temp <- unlist(strsplit(filenames, "[_]"))

hr <- temp[seq(4, length(filenames)*6, by = 6)];
min <- temp[seq(5, length(filenames)*6, by = 6)];
sec <- temp[seq(6, length(filenames)*6, by = 6)];
time <- paste0(hr, "_", min, "_", sec)

list <- list()
for(i in 1:length(time)) {
  dat.nc <- nc_open(paste0("F:/Harbour_les/les0905/wrfout_d03_2022-09-06_", time[i]))

  #plume <- ncvar_get(dat.nc, "PLUME")  # the unit is kg N2O/kg Air
  lat <- ncvar_get(dat.nc, "XLAT")
  lon <- ncvar_get(dat.nc, "XLONG")
  U <- ncvar_get(dat.nc, "U")
  V <- ncvar_get(dat.nc, "V")
  W <- ncvar_get(dat.nc, "W")

  ph <- ncvar_get(dat.nc, "PH")
  phb <- ncvar_get(dat.nc, "PHB")
  hgt <- ncvar_get(dat.nc, "HGT")

  nc_close(nc=dat.nc)
  
  # height (a.g.l) = geospatial height/9.81-terrain height
  array1 <- (ph+phb)/9.81
  array2 <- array(hgt, dim = c(ncol(hgt), nrow(hgt), dim(array1)[3]))
  array3 <- array1-array2
  
  # the range of the altitude and latitude/longitude of each airborne flight
  lower <- min(data$alt.ac, na.rm = TRUE);
  upper <- max(data$alt.ac, na.rm = TRUE)
  
  # correspond to the airborne measurements height (above the ground level)
  index <- which(array3>lower & array3<upper, arr.ind = TRUE)
  #layers <- unique(index[,3])
  layers <- min(index[,3])

  # PICK UP THE layers of LES data and convert it into a dataframe
  df <- data.frame(
      date = as.POSIXct(paste0("2022-09-06 ", hr[i], ":", min[i], ":", sec[i]), tz = "UTC"),
      lat = as.vector(lat),
      lon = as.vector(lon),
      alt = as.vector(array3[,,layers]),
      U = as.vector(U[1:836, 1:836, layers]),
      V = as.vector(V[1:836, 1:836, layers])

      #N2O = as.vector(plume[,,layers])*28.96/44*10^9,  # convert the unit of kg N2O/ kg Air to the unit of ppb
      #CH4 = as.vector(plume[,,layers])*28.96/16*10^9  # convert the unit of kg CH4/ kg Air to the unit of ppb
      )
  list[[i]] <- df
}
setwd("D:/1 PhD Studies/1 Data/LES/0905/wind")
save(list, file = "layer_25_wind.RData")

# save data into a dataframe
#write.table(les.value, "D:/1 PhD Studies/1 Data/LES/2022_09_06_LES_corresponding_to_aircore_measurements.csv", sep = ",", row.names = FALSE, col.names=TRUE)
```

```{r make animation of wind}

# setwd("D:/1 PhD Studies/1 Data/LES/0905/wind")
load("layer_25_wind.RData")

library(gganimate)
library(gifski)
library(data.table)
library(viridis)

df <- data.table::rbindlist(list[1:5]);
df <- mutate(df, ws=rWind::uv2ds(U,V)[,2], wd=rWind::uv2ds(U,V)[,1])

unique <- unique(df$date)
df.1 <- df[df$date==unique[1],]

p <- ggplot(df, mapping = aes(x = lon, y = lat, group = date, fill = ws))+
  geom_tile(width = 0.000458, height = 0.00027)+
  scale_fill_viridis()+
  labs(title = "wind speed", x = "longitude", y = "latitude", fill = "ws [m/s]")

# Animate the plot over the Month variable
p_anim <- p + transition_time(date) +
  labs(title = "time")

# Save the animation as a GIF
anim_save("layer_25_ws.gif", animation = p_anim)
```
The rscript runs very slowly. It took me about 1.5 hours to combine five time stamps into one animation. 



\newpage
# **2. load the mast measurements**
```{r}

###### information ######
# Latitude: 51.9629833°N
# Longitude: 4.0053389°E
# the height is above the ground level

mast <- read.csv("D:/1 PhD Studies/1 Data/LES/met_mast_Rotterdam.csv", skip =1, sep = ";"); 
datetime <- lubridate::ymd_hms(mast[-1, 1])
mast <- data.frame(apply(mast[-1, -1], 2, as.numeric), datetime); str(mast)


# melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H135_Ws_Q1_avg", "MMX_H130B160_Ws_Q1_avg", "MMX_H080B160_Ws_Q1_avg", "MMX_H025B160_Ws_Q1_avg", "MMX_H025B340_Ws_Q1_avg"))
# 
# melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H126_RH_Q1_avg", "MMX_H021_RH_Q1_avg"))
# 
# melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H126_Temp_Q1_avg", "MMX_H021_Temp_Q1_avg"))
# 
# ggplot(mast, mapping = aes(x = datetime, y = MMX_H126_Pair_Q1_avg))+geom_point()

melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H126B340_Wd_Q1_avg", "MMX_H126B160_Wd_Q1_avg", "MMX_H080B340_Wd_Q1_avg", "MMX_H021B160_Wd_Q1_avg"))

pdf("D:/1 PhD Studies/1 Data/LES/0905/plots/mast.data.pdf")
time <- seq(as.POSIXct("2022-09-03 00:00:00", tz = "UTC"), as.POSIXct("2022-09-06 24:00:00", tz = "UTC"), by = "1 day")
for(i in 1:4) {
  sel <- melt[melt$datetime>time[i] & melt$datetime<time[i+1], ]
  p <- ggplot(melt, mapping = aes(x = datetime, y = value, group = variable, colour = variable))+geom_point()
  print(p)
}
while (!is.null(dev.list()))  dev.off()

```


# **3. comparison with mast measurements**
## **select LES grids for comparison with mast measurements**
```{r for wind measurements}


filenames <- list.files(path = "F:/Harbour_les/les0905/", pattern = "")
temp <- unlist(strsplit(filenames, "[_]"))

hr <- temp[seq(4, length(filenames)*6, by = 6)];
min <- temp[seq(5, length(filenames)*6, by = 6)];
sec <- temp[seq(6, length(filenames)*6, by = 6)];

time <- paste0(hr, "_", min, "_", sec)

# Preallocate the list
list <- vector("list", length(time))

# Open the first file to get the necessary data
dat.nc <- nc_open(paste0("F:/Harbour_les/les0905/wrfout_d03_2022-09-05_", time[1]))

# Extract coordinates only once
lat <- ncvar_get(dat.nc, "XLAT")
lon <- ncvar_get(dat.nc, "XLONG")

# Find the closest coordinate only once
matrix <- cbind(lon = as.vector(lon), lat = as.vector(lat))
distances <- distance(matrix, t(c(4.0053389, 51.9629833)), lonlat = TRUE) # pick up the les grids for the layers 1:12 closest to the location of the mast (Latitude: 51.9629833°N Longitude: 4.0053389°E)!!!
closest_coordinate <- matrix[which.min(distances), ]
index.lon <- unique(which(lon == closest_coordinate[[1]], arr.ind = TRUE)[, 1])
index.lat <- unique(which(lat == closest_coordinate[[2]], arr.ind = TRUE)[, 2])

rm(lon, lat, matrix, distances)

# Close the initial file
nc_close(dat.nc)

for(i in seq.int(time)) {
  dat.nc <- nc_open(paste0("F:/Harbour_les/les0905/wrfout_d03_2022-09-05_", time[i]))

  U <- ncvar_get(dat.nc, "U")
  V <- ncvar_get(dat.nc, "V")

  ph <- ncvar_get(dat.nc, "PH")
  phb <- ncvar_get(dat.nc, "PHB")
  hgt <- ncvar_get(dat.nc, "HGT")

  ###################
  nc_close(nc=dat.nc)
  ###################
  
  # linearly Interpolating U component (shifted by half a grid cell in the x-direction)
  U_interpolated <- 0.5 * (U[1:(dim(U)[1] - 1), , ] + U[2:dim(U)[1], , ])

  # linearly Interpolating V component (shifted by half a grid cell in the y-direction (lat))
  V_interpolated <- 0.5 * (V[, 1:(dim(V)[2] - 1), ] + V[, 2:dim(V)[2], ])

  rm(dat.nc, U, V)
  
  # height (a.g.l) = geospatial height/9.81-terrain height
  array1 <- (ph+phb)/9.81
  array2 <- array(hgt, dim = c(ncol(hgt), nrow(hgt), dim(array1)[3]))
  array3 <- array1-array2

  rm(ph, phb, hgt, array1, array2)
  
  # linearly Interpolating height (a.g.l) (shifted by half a grid cell in the z-direction (alt))
  alt_interpolated <- 0.5 * (array3[, , 1:(dim(array3)[3]-1)] + array3[, , 2:dim(array3)[3]])

  # remove unuseful objects from environments
  rm(array3)
  
  df <- data.frame(
      datetime = as.POSIXct(paste0("2022-09-05 ", hr[i], ":", min[i], ":", sec[i]), tz = "UTC"),
      lon = closest_coordinate[[1]], 
      lat = closest_coordinate[[2]], 
      U = U_interpolated[index.lon, index.lat, 1:12],
      V = V_interpolated[index.lon, index.lat, 1:12],
      alt = alt_interpolated[index.lon, index.lat, 1:12]
    )
  list[[i]] <- df
  
  # remove unuseful objects from environments
  rm(U_interpolated, V_interpolated, alt_interpolated)
  
}
df <- do.call(rbind, list)
write.csv(df, "D:/1 PhD Studies/1 Data/LES/0905/extract_les/wind.vertical.profile.csv")

```

```{r for pressure and temperature}


filenames <- list.files(path = "F:/Harbour_les/les0905/", pattern = "")
temp <- unlist(strsplit(filenames, "[_]"))

hr <- temp[seq(4, length(filenames)*6, by = 6)];
min <- temp[seq(5, length(filenames)*6, by = 6)];
sec <- temp[seq(6, length(filenames)*6, by = 6)];

time <- paste0(hr, "_", min, "_", sec)

# Preallocate the list
list <- vector("list", length(time))

# Open the first file to get the necessary data
dat.nc <- nc_open(paste0("F:/Harbour_les/les0905/wrfout_d03_2022-09-05_", time[1]))

# Extract coordinates only once
lat <- ncvar_get(dat.nc, "XLAT")
lon <- ncvar_get(dat.nc, "XLONG")

# Find the closest coordinate only once
matrix <- cbind(lon = as.vector(lon), lat = as.vector(lat))
distances <- distance(matrix, t(c(4.0053389, 51.9629833)), lonlat = TRUE) # pick up the les grids for the layers 1:12 closest to the location of the mast (Latitude: 51.9629833°N Longitude: 4.0053389°E)!!!
closest_coordinate <- matrix[which.min(distances), ]
index.lon <- unique(which(lon == closest_coordinate[[1]], arr.ind = TRUE)[, 1])
index.lat <- unique(which(lat == closest_coordinate[[2]], arr.ind = TRUE)[, 2])

rm(lon, lat, matrix, distances)

# Close the initial file
nc_close(dat.nc)

for(i in seq.int(time)) {
  dat.nc <- nc_open(paste0("F:/Harbour_les/les0905/wrfout_d03_2022-09-05_", time[i]))

  t <- ncvar_get(dat.nc, "T") # unit:K
  p <- ncvar_get(dat.nc, "P") # unit: Pa
  pb <- ncvar_get(dat.nc, "PB") # unit: Pa
  vapor <- ncvar_get(dat.nc, "QVAPOR") # unit: Kg Kg-1

  ph <- ncvar_get(dat.nc, "PH")
  phb <- ncvar_get(dat.nc, "PHB")
  hgt <- ncvar_get(dat.nc, "HGT")

  ###################
  nc_close(nc=dat.nc)
  ###################
  
  # height (a.g.l) = geospatial height/9.81-terrain height
  array3 <- (ph+phb)/9.81-array(hgt, dim = c(ncol(hgt), nrow(hgt), 141))

  rm(ph, phb, hgt, dat.nc)
  
  # linearly Interpolating height (a.g.l) (shifted by half a grid cell in the z-direction (alt))
  alt_interpolated <- 0.5 * (array3[, , 1:(dim(array3)[3]-1)] + array3[, , 2:dim(array3)[3]])

  # remove unuseful objects from environments
  rm(array3)
  
  df <- data.frame(
      datetime = as.POSIXct(paste0("2022-09-05 ", hr[i], ":", min[i], ":", sec[i]), tz = "UTC"),
      lon = closest_coordinate[[1]], 
      lat = closest_coordinate[[2]], 
      alt = alt_interpolated[index.lon, index.lat, 1:12],
      t = t[index.lon, index.lat, 1:12],
      p = p[index.lon, index.lat, 1:12],
      pb = pb[index.lon, index.lat, 1:12],
      vapor = vapor[index.lon, index.lat, 1:12]
    )
  list[[i]] <- df
  
  # remove unuseful objects from environments
  rm(df, t, p, pb, vapor, alt_interpolated)
  
}
df <- do.call(rbind, list)
write.csv(df, "D:/1 PhD Studies/1 Data/LES/0905/extract_les/meteo.vertical.profile.csv")


```

## **vertical profiles for comparison between LES & mast measurements**
```{r visualize vertical profiles of wind}


mast <- read.csv("D:/1 PhD Studies/1 Data/LES/met_mast_Rotterdam.csv", skip =1, sep = ";"); 
datetime <- lubridate::ymd_hms(mast[-1, 1])
mast <- data.frame(apply(mast[-1, -1], 2, as.numeric), datetime)
mast <- mast[mast$datetime>=as.POSIXct("2022-09-05 12:50:00", tz = "UTC") & mast$datetime<=as.POSIXct("2022-09-05 13:26:00", tz = "UTC"),]

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# for the comparison of ws
melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H135_Ws_Q1_avg", "MMX_H130B160_Ws_Q1_avg", "MMX_H080B160_Ws_Q1_avg", "MMX_H025B160_Ws_Q1_avg", "MMX_H025B340_Ws_Q1_avg"))

alt.character <- apply(melt, 1, function(row){
  strsplit(as.character(row["variable"]), "_")[[1]][2]
})

melt <- cbind(melt, alt.character)

# select the same measurement height with different boom directions
lowest.level <- c("H025B160", "H025B340")
melt <- melt[melt$alt.character!=lowest.level[1], ]

alt.num <- apply(melt, 1, function(row){
  as.numeric(substr(row["alt.character"], start = 2, stop = 4))
})

melt <- cbind(melt, alt.num)

melt$datetime <- as.character(melt$datetime)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~



#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# for the comparison of wd
melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H126B340_Wd_Q1_avg", "MMX_H126B160_Wd_Q1_avg", "MMX_H080B340_Wd_Q1_avg", "MMX_H021B160_Wd_Q1_avg")) # wd indicates where wd come from
alt.character <- apply(melt, 1, function(row){
  strsplit(as.character(row["variable"]), "_")[[1]][2]
})

melt <- cbind(melt, alt.character)

# select the same measurement height with different boom directions
lowest.level <- c("H126B340", "H126B160")
melt <- melt[melt$alt.character!=lowest.level[2], ]

alt.num <- apply(melt, 1, function(row){
  as.numeric(substr(row["alt.character"], start = 2, stop = 4))
})

melt <- cbind(melt, alt.num)

melt$datetime <- as.character(melt$datetime)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~



les <- read.csv("D:/1 PhD Studies/1 Data/LES/0905/extract_les/wind.vertical.profile.csv")
les <- mutate(les, ws=rWind::uv2ds(U,V)[,2], wd=rWind::uv2ds(U,V)[,1])#;names(data)
les <- mutate(les, wd.1 = case_when(
  wd-180>0 ~ wd-180,
  wd-180<0 ~ wd-180+360)) # convert the degree to the number that indicates where wd come from


#pdf("D:/1 PhD Studies/1 Data/LES/0905/plots/mast&les.wind.pdf")
tiff(paste0("D:/1 PhD Studies/1 Data/LES/0905/plots/mast&les.wd.", lowest.level[1], ".tiff"), units="mm", width=300, height=200, res=300)
ggplot()+
  geom_point(les, mapping = aes(x = wd.1, y = alt, group = datetime, colour = datetime))+
  geom_path(les, mapping = aes(x = wd.1, y = alt, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "D") + # First color scale
  labs(colour = "LES")+

  # Indicate a new color scale
  ggnewscale::new_scale_color() +
  geom_point(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  geom_path(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "B")+
  labs(colour = "mast.measure")+
  ggtitle(lowest.level[1])

while (!is.null(dev.list()))  dev.off()




distHaversine(c(4.0053389, 51.9629833), c(les$lon[1], les$lat[1]))
distVincentySphere(c(4.0053389, 51.9629833), c(les$lon[1], les$lat[1]))
distGeo(c(4.0053389, 51.9629833), c(les$lon[1], les$lat[1]))
```

The ws measured at the lowest height level of 25 m mounted at the direction of 160 is only a bit larger (0.1-0.3 m/s) than that measured at 340 degree. Can be ignored in my case.
The wd measured at 126 m by the cup anemometer mounted at the direction of 160 deg has a bias of ~5 deg than that mounted at 340 deg.
The distance between the location of mast and les is around 13 m.

```{r visualize vertical profiles of pressure and temperature}

les <- read.csv("D:/1 PhD Studies/1 Data/LES/0905/extract_les/meteo.vertical.profile.csv")
p.total <- (les$p+les$pb)/100 # hpa
pot <- les$t+300 # kelvin
tair <- pot*(p.total/1000)^0.286 # kelvin
e = les$vapor*p.total/(0.622+les$vapor) # hpa
es <- 6.11*10^(2.5*10^6/461.52*(1/273.15-1/tair)) # hpa; Clausius-Clapeyron relation.
es.1 <- 6.1078*10^(17.2693882*(tair-273.16)/(tair-35.86)) # the equation proposed by Murray (1967)
RH <- e/es*100
les <- cbind(les, p.total, pot, tair, e, es, es.1, RH) # temp and pot.temp are in kelvin



mast <- read.csv("D:/1 PhD Studies/1 Data/LES/met_mast_Rotterdam.csv", skip =1, sep = ";"); 
datetime <- lubridate::ymd_hms(mast[-1, 1])
mast <- data.frame(apply(mast[-1, -1], 2, as.numeric), datetime)
mast <- mast[mast$datetime>=as.POSIXct("2022-09-06 12:16:00", tz = "UTC") & mast$datetime<=as.POSIXct("2022-09-06 12:56:00", tz = "UTC"),]
# calculate potential temperature in degree
mast <- mutate(mast,
               pot.126 = (MMX_H126_Temp_Q1_avg+273.15)*(1000/MMX_H126_Pair_Q1_avg)^0.286,
               pot.21 = (MMX_H021_Temp_Q1_avg+273.15)*(1000/(MMX_H126_Pair_Q1_avg+13))^0.286) 
mast$pot.126 <- mast$pot.126-273.15;
mast$pot.21 <- mast$pot.21-273.15




#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# for the comparison of RH and temperature
pdf("D:/1 PhD Studies/1 Data/LES/0905/plots/mast&les.meteo.pdf")

########################
# plot relative humidity
########################

  melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H126_RH_Q1_avg", "MMX_H021_RH_Q1_avg"))
  alt.character <- apply(melt, 1, function(row){
  strsplit(as.character(row["variable"]), "_")[[1]][2]
})
  melt <- cbind(melt, alt.character)
  alt.num <- apply(melt, 1, function(row){
  as.numeric(substr(row["alt.character"], start = 2, stop = 4))
})
  melt <- cbind(melt, alt.num)
  melt$datetime <- as.character(melt$datetime)

ggplot()+
  geom_point(les, mapping = aes(x = RH, y = alt, group = datetime, colour = datetime))+
  geom_path(les, mapping = aes(x = RH, y = alt, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "D") + # First color scale
  labs(colour = "LES")+

  # Indicate a new color scale
  ggnewscale::new_scale_color() +
  geom_point(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  geom_path(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "B")+
  labs(colour = "mast.measure", x = "relative humidity [%]")

########################
# plot temperature
########################

  melt <- melt(mast, id.vars = "datetime", measure.vars = c("MMX_H126_Temp_Q1_avg", "MMX_H021_Temp_Q1_avg"))
  alt.character <- apply(melt, 1, function(row){
  strsplit(as.character(row["variable"]), "_")[[1]][2]
})
  melt <- cbind(melt, alt.character)
  alt.num <- apply(melt, 1, function(row){
  as.numeric(substr(row["alt.character"], start = 2, stop = 4))
})
  melt <- cbind(melt, alt.num)
  melt$datetime <- as.character(melt$datetime)

ggplot()+
  geom_point(les, mapping = aes(x = tair-273.15, y = alt, group = datetime, colour = datetime))+
  geom_path(les, mapping = aes(x = tair-273.15, y = alt, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "D") + # First color scale
  labs(colour = "LES")+

  # Indicate a new color scale
  ggnewscale::new_scale_color() +
  geom_point(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  geom_path(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "B")+
  labs(colour = "mast.measure", x = "temp [deg]")


########################
# plot potential temperature
########################

  melt <- melt(mast, id.vars = "datetime", measure.vars = c("pot.126", "pot.21"))
  alt.num <- apply(melt, 1, function(row){
  as.numeric(substr(row["variable"], start = 5, stop = 7))
})
  melt <- cbind(melt, alt.num)
  melt$datetime <- as.character(melt$datetime)

ggplot()+
  geom_point(les, mapping = aes(x = pot-273.15, y = alt, group = datetime, colour = datetime))+
  geom_path(les, mapping = aes(x = pot-273.15, y = alt, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "D") + # First color scale
  labs(colour = "LES")+

  # Indicate a new color scale
  ggnewscale::new_scale_color() +
  geom_point(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  geom_path(melt, mapping = aes(x = value, y = alt.num, group = datetime, colour = datetime))+
  scale_color_viridis_d(option = "B")+
  labs(colour = "mast.measure", x = "potential temp [deg]")

while (!is.null(dev.list()))  dev.off()

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~





distHaversine(c(4.0053389, 51.9629833), c(les$lon[1], les$lat[1]))
distVincentySphere(c(4.0053389, 51.9629833), c(les$lon[1], les$lat[1]))
distGeo(c(4.0053389, 51.9629833), c(les$lon[1], les$lat[1]))
```




\newpage
